\documentclass[a4paper, 11pt]{article}

\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amsthm}

\usepackage{fontspec}
\usepackage{mathtools}
\usepackage{enumerate}
\usepackage{amsfonts}
\usepackage[usenames,dvipsnames,table]{xcolor}
\usepackage[
  colorlinks  = true,
  linkcolor   = black,
  citecolor   = black,
  pdfauthor   = {Ayberk\ Tosun\ and\ Mart\'{i}n\ H.\ Escard\'{o}},
  pdftitle    = {A\ Construction\ of\ the\ Patch\ Frame\ in\ Univalent\ Type\ Theory},
  pdfsubject  = {Pointfree\ topology},
  pdfkeywords = {},
  bookmarks   = false
]{hyperref}

\usepackage[
  mincrossrefs=999,
  style=numeric,
  backend=biber,
  url=false,
  isbn=false,
  doi=false,
]{biblatex}

\addbibresource{references.bib}

\newtheorem*{ex}{Exercise}
\newtheorem{lem}{Lemma}
\newtheorem{thm}{Theorem}

\theoremstyle{definition}
\newtheorem{prop}{Proposition}
\newtheorem{defn}{Definition}
\newtheorem{example}{Example}

\newcommand{\paren}[1]{\left( #1 \right)}
\newcommand{\setof}[1]{\left\{ #1 \right\}}
\newcommand{\is}{\vcentcolon\equiv}
\DeclareMathOperator{\emptyl}{\epsilon}
\DeclareMathOperator{\cons}{\colon\kern-1.1ex\colon\kern-0.4ex}
\DeclareMathOperator{\append}{\,}

%% Universe notation.
\newcommand{\UU}{\mathcal{U}}
\newcommand{\VV}{\mathcal{V}}
\newcommand{\WW}{\mathcal{W}}

%% Notation for the enumeration function in directification.
\newcommand{\dd}[1]{\mathfrak{d}(#1)}

%% Shorthand for family.
\newcommand{\Fam}[2]{\mathsf{Fam}_{#1}\left(#2\right)}

\newcommand{\define}[1]{\emph{#1}}

\newcommand{\todo}[1]{{\large\color{orange}\textsf{To-do: #1.}}}

\title{A Construction of The Patch Frame in Univalent Type Theory}
\author{Ayberk Tosun \and Mart\'{i}n H.\ Escard\'{o}}

\begin{document}

\maketitle

\begin{abstract}
  \todo{write an abstract}
\end{abstract}

\section{Preliminaries}

\begin{defn}[Family]
  A \define{$\UU$-family on a type} $A$ is a pair $(I, f)$ where $I : \UU$ and $f : I \rightarrow A$. We
  denote the type of $\UU$-families by $\mathsf{Fam}$ i.e.\ $\Fam{\UU}{A} \is \Sigma_{(I : \UU)} I \rightarrow A$.
\end{defn}

We often use the shorthand $\{ x_i \}_{i : I}$ for families.

\begin{defn}[Directed family]
  A \define{directed family on some type} $A$ is a family $(I, f)$ such that
  \begin{enumerate}[\indent (a)]
    \item $I$ is (merely) inhabited, and
    \item for every $i, j : I$, there (merely) exists some $k : I$ such that $f(k)$ is the upper
      bound of $\{ f(i), f(j) \}$.
  \end{enumerate}
\end{defn}

Our definition of a frame is parameterised by three universes: one for the carrier set, one for the
order, and one for the index type of families on which the join operation is defined. We adopt the
convention of using universe variables of $\UU$, $\VV$, and $\WW$ for these respectively.

\begin{defn}[Frame]
  A \define{$(\UU, \VV, \WW)$-frame} consists of:
  \begin{itemize}
    \item a set $| F | : \UU$,
    \item a partial order $\_\le\_\ :\ | F | \rightarrow \Omega_\VV$,
    \item a top element $\top : | F |$,
    \item a meet operation i.e.\ an operation $\_\wedge\_\ :\ | F | \rightarrow | F | \rightarrow | F |$ such that $x \wedge y$ is
      the greatest lower bound of $x$ and $y$ for every $x, y : | F |$, and
    \item a join operation i.e.\ an operation $\bigvee\_ : \mathsf{Fam}_{\WW}(| F |) \rightarrow | F |$ such that
      given a family $\{ x_i \}_{i : I}$, $\bigvee_i x_i$ is the least upper bound of $\{ x_i \}_{i : I}$;
  \end{itemize}
  such that binary meets distribute over arbitrary joins:
  \begin{equation*}
    x \wedge \bigvee_{i : I} y_i = \bigvee_{i : I} x \wedge y_i
  \end{equation*}
  for every $x : | F |$, family $\{ y_i \}_{i : I} : \mathsf{Fam}_{\WW}(| F |)$.
\end{defn}

Nuclei on a frame $F$ correspond to regular monomorphisms (in the category of locales) on the locale
corresponding to frame $F$.

\begin{defn}[Nucleus]
  A \define{nucleus on a $(\UU, \VV, \WW)$-frame} $F$ is an endofunction $j : | F | \rightarrow | F |$
  satisfying, for every $x, y : | F |$,
  \begin{itemize}
    \item \emph{meet preservation}: $j(x \wedge y) = j(x) \wedge j(y)$,
    \item \emph{inflation property}: $x \le j(x)$, and
    \item \emph{idempotency}: $j(j(x)) \le j(x)$.
  \end{itemize}
\end{defn}

An inflationary and meet-preserving endofunction that is not necessarily idempotent is called a
\define{prenucleus}. Prenuclei are closed under composition whereas this is not generally the case
for nuclei.

We write $\mathsf{Nucleus}(F)$ to denote the type of nuclei on a given frame $F$.

\begin{prop}
  Given any nucleus $F$, the type $\mathsf{Nucleus}(F)$ is an set.
\end{prop}

\begin{prop}\label{prop:nuclei-mono}
  Every prenucleus is monotonic.
\end{prop}
\begin{proof}
  Let $j : | F | \rightarrow | F |$ be a nucleus on some frame $F$ and let $x, y : | F |$ such that $x \le y$.
  We have:
  \begin{equation*}
    j(x) = j (x \wedge y) = j(x) \wedge j(y) \le j(y),
  \end{equation*}
  by meet preservation and the fact that $x \le y \leftrightarrow x \wedge y = x$.
\end{proof}

\begin{defn}[Scott-continuity]
  A function $f : | F | \rightarrow | G | $ from a $(\UU, \VV, \WW)$-frame $F$ to a $(\UU, \VV, \WW)$-frame
  $G$ is called \define{Scott-continuous} iff given any \emph{directed}
  $\{ x_i \}_{i : I} : \Fam{\WW}{| F |}$,
  \begin{equation*}
    f\left(\bigvee_{i : I} x_i\right) = \bigvee_{i : I} f(x_i).
  \end{equation*}
\end{defn}

\begin{prop}
  Every Scott-continuous function is monotonic.
\end{prop}
\begin{proof}
  Let $f : | F | \rightarrow | G |$ be a Scott-continuous function and let $x, y : | F |$ such that $x \le y$
  i.e.\ $\bigvee \{ x, y \} = y$. Note that the set $\{x, y\}$ is directed meaning we have
  \begin{equation*}
    f(x) \le \bigvee \setof{f(x), f(y)} = f\paren{\bigvee \setof{x, y}} = f(y).
  \end{equation*}
\end{proof}

\section{Meet-semilattice of nuclei}

Nuclei form a meet-semilattice when ordered pointwise.

\begin{prop}\label{defn:nuclei-semilattice}
  The type of nuclei on a given frame $F$ forms a meet-semilattice as follows:
  \begin{itemize}
    \item order: given nuclei $j$ and $k$, $j \le k \is \forall x : | F |.\ j(x) \le k(x)$,
    \item the top nucleus: $\_ \mapsto \top$, and
    \item the meet of two nuclei: $j \wedge k \is x \mapsto j(x) \wedge k(x)$.
  \end{itemize}
  It is easy to see that $j \wedge k$ is the greatest lower bound of $j$ and $k$ so it remains to show
  that $j \wedge k$ satisfies the nucleus laws. This is given in Proposition~\ref{prop:nuclei-meet}.
\end{prop}

We denote this meet-semilattice $\mathcal{N}(F)$. Let us also remark that, even though we are
primarily interested in the meet-semilattice of nuclei, we also talk about the ordering on
\emph{prenuclei} by which the same pointwise ordering is meant.

\begin{prop}\label{prop:nucl-lemma-1}
  Given any two prenuclei $j$ and $k$ on some frame $F$, $j \circ k$ is an upper bound of $\{ j, k \}$.
\end{prop}
\begin{proof}
  Given any $x : | F |$, we have that $k(x) \le j(k(x))$ by the inflation property of $j$ and that
  $j(x) \le j(k(x))$ by the monotonicity of $j$, since $x \le k(x)$ by the inflation property of $k$.
\end{proof}

\begin{prop}\label{prop:nuclei-meet}
  Given two nuclei $j$ and $k$ on some frame $F$, the function $j \wedge k \is x \mapsto j(x) \wedge k(x)$ is a
  nucleus.
\end{prop}
\begin{proof}
  The inflation property can be seen to be satisfied from the inflation properties of $j$ and $k$
  and the fact that $j(x) \wedge k(x)$ is the greatest lower bound of $j(x)$ and $k(x)$. To see that meet
  preservation holds, let $x, y : | F |$. We have:
  \begin{align*}
    (j \wedge k)(x \wedge y) &\quad\equiv\quad j (x \wedge y) \wedge k (x \wedge y)         \\
                   &\quad=\quad j(x) \wedge j(y) \wedge k(x) \wedge k(y)     \\
                   &\quad=\quad (j(x) \wedge k(x)) \wedge (j(y) \wedge k(y)) \\
                   &\quad\equiv\quad (j \wedge k)(x) \wedge (j \wedge k)(y).
  \end{align*}
  For idempotency, let $x : | F |$. We have:
  \begin{align*}
    (j \wedge k)((j \wedge k)(x)) &\quad\equiv\quad j (j(x) \wedge k(x)) \wedge k(j(x) \wedge k(x))      \\
                        &\quad=\quad j(j(x)) \wedge j(k(x)) \wedge k(j(x)) \wedge k(k(x)) \\
                        &\quad\le\quad j(j(x)) \wedge k(k(x))                     \\
                        &\quad=\quad j(x) \wedge k(x)                           \\
                        &\quad\equiv\quad (j \wedge k)(x).
  \end{align*}
\end{proof}

\begin{prop}\label{prop:sc-nuclei-semilattice}
  The type of Scott-continuous nuclei on a given $(\UU, \VV, \WW)$-frame $F$ forms a
  meet-semilattice.
\end{prop}
\begin{proof}
  The construction is the same as the one in Definition~\ref{defn:nuclei-semilattice}; the top
  element is $\top_{\mathcal{N}(F)}$ which is trivially Scott-continuous so it remains to show that the
  meet of two Scott-continuous nuclei is Scott-continuous. Consider two Scott-continuous nuclei $j$
  and $k$ on some frame $F$ and a directed family $\{ x_i \}_{i : I} : \mathsf{Fam}_{\WW}(| F |)$.
  This follows as:
  \begin{align*}
       (j \wedge k) \paren{\bigvee_{i : I} x_i}
    &\equiv j \paren{\bigvee_{i : I} x_i} \wedge k \paren{\bigvee_{i : I} x_i} & \\
    &= \paren{\bigvee_{i : I} j(x_i)} \wedge \paren{\bigvee_{i : I} k(x_i)} & [\text{Scott-continuity of $j$ and $k$}]\\
    &= \bigvee_{(i, j) : I \times I} j(x_i) \wedge k(x_i)                   & [\text{distributivity}]\\
    &= \bigvee_{i : I} j(x_i) \wedge k(x_i)                          & [\text{\dag}] \\
    &\equiv \bigvee_{i : I} (j \wedge k)(x_i).
  \end{align*}
  where, for the \dag\ step, we use antisymmetry. The backwards direction is immediate whereas the
  forwards direction follows, essentially, from the monotonicity of nuclei
  (Proposition~\ref{prop:nuclei-mono}). We omit the details.
\end{proof}

\section{Joins}

The nontrivial part of the patch frame construction is the join of a family $\{ k_i \}_{i : I}$ of
Scott-continuous nuclei as defining it pointwise,
\begin{equation*}
  \bigvee_{i : I} k_i \quad:\equiv\quad x \mapsto \bigvee_{i : I} k_i(x),
\end{equation*}
does not work. The problem is that this is not idempotent and hence not a nucleus. Our construction
(that follows Escard\'{o}~\cite{properly-injective}) is based on the idea that, if we start with a
family $\{ k_i \}_{i : I}$ of nuclei, we can consider the family
\begin{equation*}
  \left\{ k_{i_0} \circ \cdots \circ k_{i_n} \right\}_{(i_0, \cdots, i_n) : \mathsf{List}(I)},
\end{equation*}
which will always be directed. However, in a predicative setting, this works only on
Scott-continuous nuclei. Let us write this a bit more precisely as follows:

Before we proceed with the construction, let us note that we use the following notation for lists:
the empty list is denoted $\emptyl$, prepending an element $x$ onto some list $s$ is denoted $x
\cons s$, and the appending of $s$ to the end of list $t$ is denoted $s \append t$.

\begin{defn}
  Given a family $K :\equiv \{ k_i \}_{i \in I}$ of nuclei on a given $(\UU, \VV, \WW)$-frame $F$, we
  define \define{$K^*$} as the family $(\mathsf{List}(I), \mathfrak{d})$ where $\mathfrak{d}$ is
  defined as:
  \begin{align*}
    \dd{\emptyl}   \quad&:\equiv\quad \mathsf{id};  \\
    \dd{i \cons s} \quad&:\equiv\quad \dd{s} \circ k_i.
  \end{align*}
\end{defn}

\begin{prop}\label{prop:app-lemma}
  Let $K :\equiv \{ k_i \}_{i : I}$ be a family of prenuclei on a frame $F$. Given
  any $s, t : \mathsf{List}(I)$,
  \(\dd{s \append t} = \dd{s} \circ \dd{t}.\)
\end{prop}
\begin{proof}
  Straightforward induction, using function extensionality.
\end{proof}

\begin{prop}\label{prop:star-prenucleus}
  Given a family $K :\equiv \{ k_i \}_{i : I}$ of nuclei on a $(\UU, \VV, \WW)$-frame $F$, every $\alpha \in
  K^*$ is a prenucleus, that is, for every $s : \mathsf{List}(I)$, the function $\dd{s}$
  is a prenucleus
\end{prop}
\begin{proof}
  If $s = \emptyl$, we are done as it is immediate that the identity function $\mathsf{id}$ is a
  prenucleus. If $s = i \cons s'$, we need to show that $\dd{s'} \circ k_i$ is a prenucleus. For meet
  preservation, consider some $x, y : | F |$. We have that:
  \begin{align*}
    (\dd{s'} \circ k_i)(x \wedge y)
      &\quad\equiv\quad \dd{s'}(k_i(x \wedge y))                                                       \\
      &\quad=\quad \dd{s'}(k_i(x) \wedge k_i(y))                  & [\text{$k_i$ is a nucleus}]   \\
      &\quad=\quad \dd{s'}(k_i(x)) \wedge \dd{s'}(k_i(y))        & [\text{inductive hypothesis}] \\
      &\quad\equiv\quad (\dd{s'} \circ k_i)(x) \wedge (\dd{s'} \circ k_i)(y).
  \end{align*}
  For the inflation property, consider some $x : | F |$. We have that
  \begin{equation*}
    x \le k_i(x) \le \dd{s'}(k_i(x)),
  \end{equation*}
  by the inflation property of $k_i$ and the inductive hypothesis.
\end{proof}

\begin{prop}\label{prop:star-ub}
  Given a nucleus $j$ and a family $K \is \{ k_i \}_{i : I}$ of nuclei on some frame $F$, if $j$ is
  an upper bound of $K$ then $j$ is an upper bound of $K^*$.
\end{prop}
\begin{proof}
  Let $s : \mathsf{List}(I)$. If $s = \emptyl$, we have that $\mathsf{id}(x) \equiv x \le j(x)$.
  If $s = i \cons s'$, then we have
  \begin{align*}
       K^*_{s'}(K_i(x))
  \quad&\le\quad K^*_{s'}(j(x)) & [\text{monotonicity of $K^*_{s'}$ (Prop.~\ref{prop:star-prenucleus} and Prop.~\ref{prop:nuclei-mono})}] \\
  \quad&\le\quad j(j(x))        & [\text{inductive hypothesis}] \\
  \quad&\le\quad j(x).          & [\text{idempotency of $j$}]
  \end{align*}
\end{proof}

\begin{prop}
  Given a family $\{ k_i \}_{i : I}$ of Scott-continuous nuclei, every
  prenucleus $\alpha \in K^*$, is Scott-continuous
\end{prop}
\begin{proof}
  In the base case of $s = \emptyl$, it is trivial that the identity
  prenucleus is Scott-continuous. For the case of $s = i \cons s'$, let
  $\{ x_i \}_{i : I}$ be a directed family on $F$. The result follows equationally
  as follows:
  \begin{align*}
    (\dd{s'} \circ k_i) \left(\bigvee_i x_i\right)
    &\quad\equiv\quad \dd{s'}\left(k_i \left( \bigvee_i x_i \right)\right) & \\
    &\quad=\quad \dd{s'}\left(\bigvee_{i : I} \left( k_i(x_i) \right)\right) & [\text{Scott-continuity of $k_i$}]\\
    &\quad=\quad \bigvee_{i : I} \dd{s'}(k_i(x_i)) & [\text{inductive hypothesis}].
  \end{align*}
  Note that to be able to appeal to the inductive hypothesis, it must be shown that
  $\{ k_i(x_i) \}_{i : I}$ is a directed family which follows from \ldots \todo{complete}
\end{proof}

\begin{prop}
  Given a family $K :\equiv \{ k_i \}_{i : I}$ of nuclei on some frame $F$, the family $K^*$ is directed.
\end{prop}
\begin{proof}
  $K^*$ is always inhabited by $\dd{\emptyl}$. Upwards-closure also holds since, given $s, t :
  \mathsf{List}(I)$, $\dd{s \append t}$ is the upper bound of $\{ \dd{s}, \dd{t} \}$:
  $\dd{s \append t} = \dd{s} \circ \dd{t}$ (by Proposition~\ref{prop:app-lemma}) which is the upper
  bound of $\{ \dd{s}, \dd{t} \}$ by Proposition~\ref{prop:nucl-lemma-1}.
\end{proof}

To be able to define the patch frame on $F$, we will also need some lemmas about nuclei in general.

\begin{prop}
  Given a nucleus $j$ on some frame $F$ and a family $K \is \{ k_i \}_{i : I}$ of nuclei on $F$, if
  we denote by $L$ the set $\{ j \wedge k ~|~ k \in K \}$, we have that $L^*_{s}$ is a lower bound of
  $\{ K^*_{s}, j \}$.
\end{prop}
\begin{proof}
  Let $s : \mathsf{List}(I)$ and $x : | F |$. In the base case of $s \equiv \emptyl$, we are done
  as both sides of the inequality reduce to the application of $\mathsf{id}(x)$. If we have
  $s \equiv i \append s'$, we have that
  \begin{align*}
    L^*_{i \cons s'}(x)
      \quad\equiv\quad L^*_{s'}(L_i(x))
     &\quad\equiv\quad L^*_{s'}(j(x) \wedge k_i(x)) \\
     &\quad\le\quad K^*_{s'}(j(x) \wedge k_i(x)) & [\text{inductive hypothesis}] \\
     &\quad\le\quad K^*_{s'}(j(x)) \wedge K^*_{s'}(k_i(x)) & [K^*_{s'}\ \text{is a prenucleus}] \\
     &\quad\le\quad K^*_{s'}(k_i(x)),
  \end{align*}
  and that
  \begin{align*}
    L^*_{i \cons s'}(x)
    \quad\equiv\quad L^*_{s'}(L_i(x)) 
    &\quad\equiv\quad L^*_{s'}(j(x) \wedge k_i(x)) & \\
    &\quad\le\quad j(j(x) \wedge k_i(x)) & [\text{inductive hypothesis}] \\
    &\quad\le\quad j(j(x)) \wedge j(k_i(x)) & [\text{$j$ preserves meets}]\\
    &\quad\le\quad j(j(x)) & \\
    &\quad=\quad j(x), & [\text{$j$ is idempotent}]
  \end{align*}
  which is to say $L^*_{i \cons s'}(x)$ is lower than both of $K^*_{i \cons s'}(x)$ and $j(x)$.
\end{proof}

\begin{defn}[Join of a family of Scott-continuous nuclei]
  Let $K \is \{ k_i \}_{i : I}$ be a family of Scott-continuous nuclei. Its join is given by
  the operation $\bigvee^N$ defined as:
  \begin{equation*}
    \bigvee^N_{i} k_i \quad\is\quad x \mapsto \bigvee \left\{ \alpha(x) ~|~ \alpha \in K^* \right\}.
  \end{equation*}
  We need to show that $\bigvee^N_{i} k_i$ is
    (a) a nucleus,
    (b) Scott-continuous, and
    (c) the least upper bound of $K$.

  \paragraph{(a).} The inflation property is direct. For meet preservation, consider some
  $x, y : | F |$. We have:
  \begin{align*}
         \left(\bigvee^N_{i} k_i\right)(x)
    &\quad\equiv\quad \bigvee_{\alpha \in K^*} \alpha(x \wedge y)                                                                   \\
    &\quad=\quad \bigvee_{\alpha \in K^*} \alpha(x) \wedge \alpha(y)                                & [\text{$\alpha$ is a prenucleus}]  \\
    &\quad=\quad \bigvee_{\beta, \gamma \in K^*} \beta(x) \wedge \gamma(y)                             & [\text{\todo{complete}}]      \\
    &\quad=\quad \paren{\bigvee_{\beta \in K^*} \beta(x)} \wedge \paren{\bigvee_{\gamma \in K^*} \gamma(y)}    & [\text{distributivity}]       \\
    &\quad\equiv\quad \paren{\bigvee^N_{i : I} k_i}(x) \wedge \paren{\bigvee^N_{i : I} k_i}(y).
  \end{align*}
  For idempotency, let $x : | F |$. We have that:
  \begin{align*}
    \left(\bigvee^N_{i} k_i\right)\left(\left(\bigvee^N_{i} k_i\right)(x)\right)
    &\quad\equiv\quad \bigvee \setof{ \bigvee \setof{ \alpha(\beta(x)) ~|~ \beta in K^* } ~|~ \alpha \in K^* } \\
    &\quad\le\quad \bigvee_{\alpha, \beta \in K^*} \alpha(\beta(x)) & [\text{\todo{explain}}]\\
    &\quad\le\quad \bigvee_{\alpha \in K^*} \alpha(x) & [\text{\todo{explain}}]\\
    &\quad\equiv\quad \paren{\bigvee^N_i k_i}(x).
  \end{align*}

  \paragraph{(b).} Let $U \is \{ x_j \}_{j : J}$ be a directed family over $| F |$. Then
  \begin{align*}
       \bigvee \setof{ \alpha\left(\bigvee_j x_j\right) ~|~ \alpha \in K^* }
  &= \bigvee \setof{ \bigvee \setof{ \alpha(x_j) ~|~ x_j \in U } ~|~ \alpha \in K^* }  & [\text{Scott-continuity of $\alpha$}] \\
  &= \bigvee \setof{ \bigvee \setof{ \alpha(x_j) ~|~ \alpha : K^* } ~|~ x_j \in U }, & [\text{joins commute}]           \\
  \end{align*}
  as required.

  \paragraph{(c).} The fact that $\bigvee^N_i k_i$ is an upper bound of $K$ is easy to verify:
  given some $k_i$ and $x : | F |$, $k_i(x) \in \{ \alpha(x) ~|~ \alpha \in K^* \}$ since $k_i \in K^*$. To see that
  it is \emph{the least} upper bound, consider a Scott-continuous nucleus $j$ that is an upper bound
  of $K$. Let $x : | F |$. We need to show that $\left(\bigvee^N_i k_i\right)(x) \le j(x)$. We know by
  Proposition~\ref{prop:star-ub} that $j$ is an upper bound of $K^*$, since it is an upper bound of
  $K$, which is to say $K^*_{s}(x) \le j(x)$ for every $s : \mathsf{List}(I)$ i.e.\ $j(x)$ is an
  upper bound of the family $\setof{ \alpha(x) ~|~ \alpha \in K^* }$. Since $\left(\bigvee^N_i k_i\right)(x)$ is the
  least upper bound of this family by definition, it follows that it is below $j(x)$.
\end{defn}

\begin{prop}[Distributivity]
  Given a nucleus $j$ and a family of nuclei $K \is \{ k_i \}_{i : I}$ on some frame $F$, we have
  that $j \wedge \left(\bigvee_{i : I} k_i\right) = \bigvee_{i : I} j \wedge k_i$.
\end{prop}
\begin{proof}
  \todo{complete the proof}
\end{proof}

\printbibliography

\end{document}
